Security vs. Maintainability: Fixing Vulnerabilities Obfuscates your Code\\ \thanks{Identify applicable funding agency here. If none, delete this.}

### 2019-01-23 paper/ICPC19/icpc19.tex
merge

Add a point for motivation with one of the examples of the poster.

>>>>

The international standard ISO/IEC 25010:2011 breaks down software quality into eight characteristics: maintainability,
functional suitability, performance efficiency, compatibility, usability, reliability, security,
and portability. This paper focuses solely on maintainability.

\begin{framed}
\textit{\textbf{RQ1} What is the impact of fixing vulnerabilities to improve security }
\end{framed}
